surfing

### 2023-11-01 inst/mann_whitney_wilcoxon.Rmd
consistentification

---
title: "Generalizing the Mann-Whitney-Wilcoxon test with `hyper3` objects"
author: "Robin K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

>>>>

---
title: "Generalizing the Mann-Whitney-Wilcoxon test with `hyper3` objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

### 2023-11-01 inst/red_bus_blue_bus.Rmd
consistentification

---
title: "Red bus, blue bus; and the choice between Florida, California, and Florida plus a nickel"
output: pdf_document
bibliography: chess.bib
---

>>>>

---
title: "Red bus, blue bus; and the choice between Florida, California, and Florida plus a nickel"
output: pdf_document
bibliography: hyper2.bib
---

### 2023-11-01 inst/surfing.Rmd
name all chunks and cache the slow ones
consistentification

---
title: "surfing"
output: bookdown::html_document2
bibliography: chess.bib
---

@@

```{r scomp3maxp, cache=TRUE}
scomp3
maxp(scomp3)
specificp.gt.test(scomp3,'S',0,n=100)
````

>>>>

---
title: "surfing"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

```{r scomp3maxp, cache=TRUE}
scomp3
maxp(scomp3)
specificp.gt.test(scomp3,'S',0,n=100)
```
